%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSimple}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textit{\small{#5}}  & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://moein.xyz/}{\Large Moein Hosseini}} & Email : \href{mailto:moein7tl@gmail.com}{moein7tl@gmail.com}\\
  \href{http://moein.xyz/}{http://moein.xyz} & Mobile : +98-912-468-1859 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tap30}{Tehran, Iran}
      {Senior Data Engineer}{Dec 2018 - Present}{ Fastest-growing and second carpool player in Iran (Uber of Iran)}
      \resumeItemListStart
        \resumeItemSimple{Lead the team of 3 to build and maintain a  scalable and fault-tolerance data warehouse and computation stack.}
		\resumeItemSimple{Working closely with BI and backend teams to make sure that the cluster meets business requirements.}
		\resumeItemSimple{Built synchronization services to makes data warehouse synchronized with production databases using Spark.}
		\resumeItemSimple{Setup and manage data pipelines and reporting system for ten of thousands of jobs per day using Airflow.}           
		\resumeItemSimple{Built stream processing application responsible for schema inference, event persistence and automatically creating Hive tables using Spark and Kafka.}           		
      \resumeItemListEnd
%---- BisPhone ----    
    \resumeSubheading
      {BisPhone}{Tehran, Iran}
      {Technical Product Manager (Alongside with Data Engineering role
)}{Mar 2018 - Dec 2018}{Optimized messaging and calls application with almost 3 million users}
    \resumeItemListStart
        \resumeItemSimple{Design RPC level APIs between microservices and exposed API to clients using SARF and Protobuf.}
        \resumeItemSimple{Design the end-to-end encryption protocol based on Diffie-Hellman and AES algorithms.}        
    	\resumeItemSimple{Working closely with C level people and all technical teams to define a technical road map of product, minimize technical debts during releases and divide features to deliverable tasks.}
    \resumeItemListEnd	
%---- BisPhone ----        
    \resumeSubheading
      {BisPhone}{Tehran, Iran}
      {Data Engineer / Big Data Developer}{Dec 2016 - Dec 2018}{}     
    \resumeItemListStart
        \resumeItemSimple{Count unique users interactions to contents using approximately algorithms, Flink, Kafka and Cassandra.}
    	\resumeItemSimple{ETL data to new version of application during big bang migration from SQL based DBs to Cassandra using Spark.}
    	\resumeItemSimple{Contribution to p2p messaging, message broadcasting and file storage services using Scala and Akka.} 
    	\resumeItemSimple{Built a batch service to calculate system stats from various sources and publish it on EK stack using Spark.}  	
    \resumeItemListEnd	
%---- Hunger Station ----    
    \resumeSubheading
      {HungerStation}{Remote, Saudi Arabia}
      {Software Developer}{Nov 2015 - Mar 2016}{The largest online food court in Saudi Arabia and Bahrain}    
    \resumeItemListStart
    	\resumeItemSimple{Add some features to REST APIs. Furthermore, increment the response time by adding a Redis based cache layer.}    	
    \resumeItemListEnd	      
%---- Persian Blog ----
    \resumeSubheading
      {PersianBlog}{Tehran, Iran}
      {Software Developer}{May 2014 - Dec 2014}{The first blogging platform in Persian}
    \resumeItemListStart
    	\resumeItemSimple{Development the core and the panel of PPC advertisment platform using PHP, NodeJS, MongoDB and RabbitMQ}
    \resumeItemListEnd	 
%---- Shiveh Co ----      
    \resumeSubheading
      {ShivehCo}{Tehran, Iran}
      {Junior Web Developer}{Jun 2013 - May 2014}{A pioneer company in the GIS and realtime tracking systems.}     
      \resumeItemListStart
        \resumeItemSimple{Contribution to the main project and add real-time car tracking and alerting features using PHP and MySQL.}               
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Scala, Java, Python, SQL}
    \resumeSubItem{Technologies}{Spark, Kafka, Hadoop, Flink, Ambari, Airflow, Zookeeper, Cassandra, Postgres}
  \resumeSubHeadingListEnd
  
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amirkabir University of Technology - Tehran Polytechnic}{Tehran, Iran}
      {Master of Science, Information Technology}{2015 -- 2018}{}
    \resumeSubheading
      {K. N. Toosi University of Technology}{Tehran, Iran}
      {Bachelor of Science, Computer Engineering}{2010 -- 2015}{}
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Notable Open Source Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Airflow On Ambari}{Mpack package to setup and monitor Celery based Airflow or Ambari (Ambari extension)}
    \resumeSubItem{RabbitMQ On Ambari}
      {Setup, configure and monitor single node RabbitMQ server on Ambari (Ambari extension)}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Volunteer Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AISEC}{Guangzho, China}
      {Volunteer University Exchange Student}{Jul 2016 - Aug 2016}{}
    \resumeItemListStart
    	\resumeItemSimple{Working as a volunteer in Guangzhou to improve general knowledge of Chinese migrant workers in the international team. This project helped me to develop my leadership and communication skills in the multi-culture environment.}
    \resumeItemListEnd	 		
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}